A Survey of Range-Only SLAM Techniques and Sensors

### 2018-02-19 Paper.tex
Added Conclusion

	\section{Introduction} 
		The Simultaneous Localization and Mapping (SLAM) problem is a common aspect of many autonomous robotics applications. SLAM involves estimating the pose of a mobile robot and building a map of its environment with no a priori information. The SLAM problem is a chicken-and-egg type problem, where the pose of the robot is with respect to a global frame, or map, and building a map requires knowledge of the robot's location. There are many algorithms used to solve this problem, most using a landmark-based approach. Landmarks are distinguishable feature in the environment which can be observed through devices such as a camera or a laser rangefinder. Said devices are used to estimate the distance and orientation of the landmark relative to the robot. As the robot traverses the environment it continues to observe and collect landmarks. The sensed distance and angle from each landmark is combined with odometry readings to get an refined estimation of the robot pose and map. 
		%It can continue observing that landmark, as well as collecting new landmarks, and using the sensed distances and angles combined with odometry readings to refine its estimation of the robot's pose and map. 
		In most SLAM applications, references to the map is synonymous with the locations and features of the landmarks.

@@

		This paper surveys state of the art RO-SLAM applications. Before discussing RO-SLAM techniques, the different types of range sensors are introduced in Section \ref{range only sensors}, followed by initialization of these beacons in Section \ref{beacon initialization}. Solutions to the RO-SLAM state estimation problem are covered in Section \ref{methods and their implementations}. Finally, the conclusion in Section \ref{conclusion} closes with final thoughts regarding the state of the field of RO-SLAM.

	\section{range only sensors}
	\label{range only sensors}
		There are a variety of range sensors which can be utilized for RO-SLAM. These range sensors refer to any device which involves a signal transmission that can be used for the range estimation without line of sight. The most popular beacons can largely be broken down into two categories: acoustic based and radio frequency based. These beacons serve as landmarks within larger SLAM algorithms. The following section surveys the different types of sensors which can be utilized as range beacons.

@@

		\subsection{Radio Frequency}
			Radio frequency encompass a massive spectrum of devices capable of transmitting or receiving transmission on the electromagnetic frequency. There are two methods primarily utilized to determine distance from radio frequency. One is by examining the received signal strength indicator (RSSI) and the other is the by measuring the time of flight of the signal. A system presented by \cite{Padmanabhan2000} processes RF signal strength and utilizes nearest neighbors heuristics to achieve localization based on said signal strength.  \cite{Kurth2003a} describes a method for using very small RF tags as beacons throughout the environment.  As a mobile robot moves throughout an environment it emits a query to which any RF tags that are within the transmission range respond. The robot then estimates the distance to the tag based on the delay. The response from the RF tags include a data tag which contains a unique ID number.

@@

		\subsection{Delayed/Offline initializations}
			These are methods that perform delayed localizations  where initially the robot moves around offline collects some measurements and then initializes the location of the landmarks. This can be undersirable as it causes a delay in the localization of the robot whenever there is a immediate real time application such as in autonomous vehicles. Localization can be performed only once a accurate estimations of the beacons are made. There are several offline algorithms that perform localization such as the least squares approach in \cite{Newman}, a posed based ekf as mentioned in \cite{Webster2012}, a moving horizon estimation as mentioned in \cite{Vallicrosa2014a} etc. The most popular ones are mentioned below.

@@

	\subsubsection{Particle filter}
		Particle filters takes a probabilistic approach to estimating the initial location of the beacons. As mentioned in \cite{Thrun2002a}, initially the entire space is represented by particles. Particles refer to collection of sample states. These particles are resampled based on importance weights every iteration. There are several resampling methods mentioned in \cite{Li2015}. Eventually the particle set converges to the accurate location of the beacons. Although this method of localization can be computationally expensive it is preferred whenever the noise involved is non Gaussian.

@@

	\section{Conclusion}
	\label{conclusion}

>>>>

	\section{Introduction} 
		The Simultaneous Localization and Mapping (SLAM) problem is a common aspect of many autonomous robotics applications. SLAM involves estimating the pose of a mobile robot and building a map of its environment with no a priori information. The SLAM problem is a chicken-and-egg type problem, where the pose of the robot has to be with respect to a global frame, or map, and building a map requires knowledge of the robot's pose. There are many algorithms used to solve this problem, most using a landmark-based approach. Landmarks are distinguishable feature in the environment which can be observed through devices such as a camera or a laser rangefinder. Said devices are used to estimate the distance and orientation of the landmark relative to the robot. As the robot traverses the environment it continues to observe and collect landmarks. The sensed distance and angle from each landmark is combined with odometry readings to get an refined estimation of the robot pose and map. 
		%It can continue observing that landmark, as well as collecting new landmarks, and using the sensed distances and angles combined with odometry readings to refine its estimation of the robot's pose and map. 
		In most SLAM applications, references to the map is synonymous with the locations and features of the landmarks.

@@

		This paper surveys state of the art RO-SLAM applications. Before discussing RO-SLAM techniques, the different types of range sensors are introduced in Section \ref{range only sensors}, followed by initialization of range beacons in Section \ref{beacon initialization}. Solutions to the RO-SLAM state estimation problem are covered in Section \ref{methods and their implementations}. Finally, the conclusion in Section \ref{conclusion} closes with final thoughts regarding the state of the field of RO-SLAM.

	\section{range only sensors}
	\label{range only sensors}
		There are a variety of sensors which can be utilized as range beacons for RO-SLAM. These range sensors refer to any device which involves a signal transmission that can be used for the range estimation without line of sight. The most popular sensors can largely be broken down into two categories: acoustic based and radio frequency based. These beacons serve as landmarks within larger SLAM algorithms. The following section surveys the different types of sensors which can be utilized as range beacons.

@@

		\subsection{Radio Frequency}

			Radio frequency encompass a extensive spectrum of devices capable of transmitting or receiving using radio frequencies (RF). There are two methods primarily utilized to determine distance from radio frequency. One is by examining the received signal strength indicator (RSSI) and the other is the by measuring the time of flight of the signal. A system presented by \cite{Padmanabhan2000} processes RF signal strength and utilizes nearest neighbors heuristics to achieve localization based on said signal strength.  \cite{Kurth2003a} describes a method for using very small RF tags as beacons throughout the environment.  As a mobile robot moves throughout an environment it emits a query to which any RF tags that are within the transmission range respond. The robot then estimates the distance to the tag based on the delay. The response from the RF tags include a data tag which contains a unique ID number.

@@

		\subsection{Delayed/Offline initializations}
			Delayed/offline initializations are methods which attempt to localize the beacon prior to incorporating it into the active SLAM algorithm. Some SLAM algorithms require an approximate location of each landmark before being incorporated into the algorithm. Since beacons only provide range data, the location of the beacon is not known upon first observation, and must be initialized. These processes which determine the initial estimated location of the beacon before being added to the SLAM algorithm are known as delayed or offline initializations. These initialization methods can be undesirable as they require the SLAM algorithm to run without corrective measurements until the first beacon is initialized. Presented in this section are the most prevalent methods for offline beacon initialization.

@@

			\subsubsection{Particle filter}
				Particle filters takes a probabilistic approach to estimating the initial location of the beacons. As mentioned in \cite{Thrun2002a}, initially the entire space is represented by particles. Particles refer to collection of sample states. These particles are re-sampled based on importance weights every iteration. There are several re-sampling methods mentioned in \cite{Li2015}. Eventually the particle set converges to the accurate location of the beacons. Although this method of localization can be computationally expensive it is preferred whenever the noise involved is non Gaussian.

			\subsubsection{Other Methods}
			 	The methods presented above tend to be the more common approaches, however, there are several offline algorithms that perform offline localization. A least squares approach is described in \cite{Newman}, a posed-based EKF (Extended Kalman Filter) method is mentioned in \cite{Webster2012}, and a moving horizon estimation is presented in \cite{Vallicrosa2014a}. These methods have also proven effective for the beacon types used in their respective applications.

@@

	\section{Conclusion}
	\label{conclusion}
	This paper has introduced the motivation and practicality of range-only SLAM approaches. The variety of sensors used as range only beacons has been surveyed, along with initialization methods for their incorporation into the common SLAM algorithms. The variety of SLAM algorithms as they apply to range-only sensor data are surveyed here as well with a focus on the techniques that differentiate them and highlighting their strengths and weaknesses.

	Given the maturity of SLAM as a research field, the area of RO-SLAM still has lots of area to explore. Most of the common methodologies presented here focus on adapting traditional SLAM algorithms to accommodate only range data. While these adapted methods have been proven successful, there is still more research that can be conducted towards solving the RO-SLAM problem with uniques solutions which can subvert the need for offline beacon initialization and models designed to handle the multipath errors which plague range sensors.
